Robustness of MinD oscillation in \emph{Escherichia coli} with diverse cell shapes

### 2014-09-05 paper/paper.tex
updating for meeting Tested everything on wentworth.
beautify arrow plot for paper Tested everything on bennet.

\begin{figure}
  \includegraphics[width=\columnwidth]{../data/shape-randst/0_25-18_50-18_50-95_00-15_00-full_array/plots/box-plot_D}
  \includegraphics[width=\columnwidth]{../data/shape-randst/0_25-18_50-18_50-95_00-15_00-exact/plots/box-plot_D}
  \caption{A comparison of our box plots that show a disparity between
    the behavoir of the stochastic and deterministic simulations in
    our Mannik cells.  The deterministic show a regular, robust
    oscillatory behavoir between the two ends of the cell. The
    stochastic simulation do show a general back and forth tendency
    between two ends of the cell, but it is not robust and tends to
    break down.}
  \label{box-mannik}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[width=\columnwidth]{../paper/plot-ave}
  \caption{Arrows depicting global maxima in space and local maxima in
    time overlayed on color plots of time averaged total MinD density.
    A density threshold is chosen and only maxima above this threshold
    are shown. The plots serve to illistrate what is observed in our
    movies.  The simulation time covered in these is 1000 seconds
    \fixme{this is not true yet - need to change the data once its
      finished right now 2 of them are 1000 the others are like 980}.
    The top row shows plots published by Mannik of the MinD maxima
    behavoir and the bottom two rows show our pancake shapes that are
    designed to have the same shape.  The middle row shows results
    from the stochastic simulation and the bottom shows results from
    the deterministic.  We can see that the stochastic method shows
    behavoir that is similar to experiment while the deterministic
    method shows maximization that is too regular and robust.}
  \label{randst-plot-ave}
\end{figure}

>>>>

\begin{figure}
  \includegraphics[width=\columnwidth]{../data/shape-randst/0_25-18_50-18_50-95_00-15_00-full_array/plots/box-plot_D}
  \includegraphics[width=\columnwidth]{../data/shape-randst/0_25-18_50-18_50-95_00-15_00-exact/plots/box-plot_D}
  \includegraphics[width=\columnwidth]{../data/shape-randst/0_25-18_60-28_60-94_00-15_00-full_array/plots/box-plot_D}
  \includegraphics[width=\columnwidth]{../data/shape-randst/0_25-18_60-28_60-94_00-15_00-exact/plots/box-plot_D}
  \caption{A comparison of our box plots that show a disparity between
    the behavoir of the stochastic and deterministic simulations in
    our Mannik cells.  The deterministic show a regular, robust
    oscillatory behavoir between the two ends of the cell. The
    stochastic simulation do show a general back and forth tendency
    between two ends of the cell, but it is not robust and tends to
    break down.}
  \label{box-mannik}
\end{figure}

@@

\begin{figure*}
  \centering
  \includegraphics[width=\textwidth]{../paper/plot-ave}
  \caption{\fixme{Look into unifying the color scale, and adding a
      scale bar.} Arrows depicting global maxima in space and local
    maxima in
    time overlayed on color plots of time averaged total MinD density.
    A density threshold is chosen and only maxima above this threshold
    are shown. The plots serve to illistrate what is observed in our
    movies.  The simulation time covered in these is 1000 seconds
    \fixme{this is not true yet - need to change the data once its
      finished right now 2 of them are 1000 the others are like 980}.
    The top row shows plots published by Mannik of the MinD maxima
    behavoir and the bottom two rows show our pancake shapes that are
    designed to have the same shape.  The middle row shows results
    from the stochastic simulation and the bottom shows results from
    the deterministic.  We can see that the stochastic method shows
    behavoir that is similar to experiment while the deterministic
    method shows maximization that is too regular and robust.}
  \label{randst-plot-ave}
\end{figure*}
